Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-04-04 article.tex
Format Latex

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

@@

\hypertarget{versatile-modelling-and-simulation-of-dynamical-systems-with-poincaruxe9}{%
\subsection{Versatile modelling and simulation of dynamical systems with
Poincaré}\label{versatile-modelling-and-simulation-of-dynamical-systems-with-poincaruxe9}}

@@

\hypertarget{extensible-definition-of-reaction-networks-using-simbio}{%
\subsection{Extensible definition of reaction networks using
SimBio}\label{extensible-definition-of-reaction-networks-using-simbio}}

@@

\hypertarget{reproducibility-and-performance}{%
\subsection{Reproducibility and
performance}\label{reproducibility-and-performance}}

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

\hypertarget{resources}{%
\section{Resources}\label{resources}}

>>>>

\hypertarget{introduction}{
  \section{Introduction}
  \label{introduction}
}

@@

\hypertarget{results}{
  \section{Results}
  \label{results}
}

@@

\hypertarget{versatile-modelling-and-simulation-of-dynamical-systems-with-poincaruxe9}{
  \subsection{Versatile modelling and simulation of dynamical systems with Poincaré}
  \label{versatile-modelling-and-simulation-of-dynamical-systems-with-poincaruxe9}
}

@@

\hypertarget{extensible-definition-of-reaction-networks-using-simbio}{
  \subsection{Extensible definition of reaction networks usingSimBio}
  \label{extensible-definition-of-reaction-networks-using-simbio}
}

@@

\hypertarget{reproducibility-and-performance}{
  \subsection{Reproducibility andperformance}
  \label{reproducibility-and-performance}
}

@@

\hypertarget{discussion}{
  \section{Discussion}
  \label{discussion}
}

@@

\hypertarget{resources}{
  \section{Resources}
  \label{resources}
}
